---
title: "Project 2"
---

```{r Z, include=FALSE, eval = FALSE}
rmarkdown::render("C:/Users/Bridget/OneDrive/R_Scripts/repos/brknapp.github.io/_Rmd/2022-07-09-project2-blog-post.Rmd",
                  output_format = "github_document",
                  output_dir = "C:/Users/Bridget/OneDrive/R_Scripts/repos/brknapp.github.io/_posts/",
                  output_options = list(html_preview=FALSE) 
)
```

```{r X, include=FALSE, eval = TRUE}
knitr::opts_chunk$set(fig.path = "C:/Users/Bridget/OneDrive/R_Scripts/repos/brknapp.github.io/images")
```

I need to add two links: username.github.io/repo-name site and the repo itself

[GitHub Pages Repo](https://brknapp.github.io/Project_1/)  <br>
[Regular Repo](https://github.com/chsueh2/ST558-Project2)

For Project 2, I practiced summarizing data with an exploratory data analysis (EDA), creating linear regression and ensemble tree-based models, and automating Markdown reports. 

# What Would I  Do Differently?

At first, I struggled to do the EDA because I did not know where to start or which variables to focus on. I began by making graphs that just focused on one or two variables. I realized that I would need to do this analysis for all of the variables (including the numeric and categorical). At first, my EDA did not flow very well because it did not tell a story about the entire data set. My partner helped me set up a plan for my EDA, which helped it flow better (e.g., start with graphing the response variable and then graph the rest of the variables). I then learned how to make multiple graphs (one for each variable) at the same time so that we could compare them. If I was able to do this part again, I would start by planning out my EDA and deciding which variables to visualize first. Then, I would prepare tables/graphs to explain each variable.

# What was the Most Difficult Part?

The most difficult part of this project was understanding how to automate this process. I remember learning how to do this in RMarkdown in lecture by setting parameters and using the apply and render functions. I was not sure how to apply this to GitHub. My partner showed me how to do this with a function.

# What are the Big Take-Aways from this Project?

Every model has its upsides and downsides. For example, a tree model is more flexible than a simple linear regression model (SLR) because a tree model splits up the predictor region and averages all the values within each region for the prediction whereas an SLR fits one line for the entire data set. This gives a tree model more flexibility than an SLR, but it will increase the variance.




